---
title: "LinearRegression"
author: "Johnson Adebayo_SCV1007 (Cohort 1)"
date: "4/3/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Source: https://data-flair.training/blogs/r-linear-regression-tutorial/

1. Importing the Dataset
```{r}
data("cars")
View(cars)
```

```{r}
str(cars)
```

2. Visualising Linearity using Scatterplots
```{r}
scatter.smooth(x=cars$speed, y = cars$dist, xlab ="Speed",ylab ="Distance", main="Scatter Plot of Distance against Speed")
```

3. Measuring Correlation Coefficient
# The result below shows that there is a strong positive correlation btw speed and distance
```{r}
cor(cars$speed, cars$dist) #Finding Correlation between speed and distance
```

4. Building the Linear Model
```{r}
# fitted linear model, dist-dependent variable, speed-independent variable
linear_model <- lm(dist~speed, data = cars)
#summary(linear_model)
print(linear_model)
```

5. Diagnosing the Linear Model
After building our model, we can diagnose it by checking if it is statistically significant. In order to do so, we make use of the summary() function as follows:
# The model is statistically significant (there is significant relationship btw dist and speed) because the null hypothesis is rejected (bcos p-value is 1.49e-12 $ less than 0.5)
```{r}
summary(linear_model)
```

6. Calculating Standard Error and F – statistic


```{r}
Model_Summary <- summary(linear_model)
Model_Coefficients <- Model_Summary$coefficients
std_error <- Model_Coefficients["speed", "Std. Error"]
print(std_error)
```

```{r}
f_stat <- summary(linear_model)$fstatistic
f_stat
```



```{r}
linear_model$coefficients
```

```{r}
(Model_Summary$coefficients)
```


```{r}
Model_Coefficients["speed","t value"]
```


```{r}
t1 <- summary(linear_model)$coefficients
t1
```


```{r}
lm_pred <- predict(linear_model, cars)
df_lm <- data.frame(cars$dist,lm_pred)
View(df_lm)
```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```



