---
title: "Population of States in Nigeria"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
    storyboard: TRUE
    
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(ggplot2)
library(ggpubr)
```

```{r}
nig_pop <- read.csv("nigeria-population-by-state.csv")
nig_pop2 <- read.csv("nigeria-population-by-state.csv", row.names = 1)
#View(nig_pop2)
```


Sidebar {.sidebar data-width=250}
================================================

### Selection Panel
```{r}
selectInput("state","Select State",choices =nig_pop$State, multiple = FALSE )

renderText({
  
  paste(input$state, "Population: ", nig_pop[nig_pop$State==input$state,2])
  
})

```


Population Gauge {.storyboard data-navmenu="Menu"}
=============================================================================

### Population of State in Number
```{r}
#Population Gauge{data-navmenu="Menu"} # to used the navbar as a "menu"

#rate <- computeContactRate()
renderGauge({
  #if(input$submit>0){
    
    gauge(nig_pop[nig_pop$State==input$state,2] , min = 0, max =20000000,label= "Population",gaugeSectors(success = c(1,9999999), warning = c(10000000,15000000), danger = c(15000001, 20000000)))
    
 # }
  
  
})

```


### Population of State in Percentage
```{r}
#rate <- computeContactRate()
renderGauge({
  #if(input$submit>0){
    
    gauge(round(((nig_pop[nig_pop$State==input$state,2]/sum(nig_pop$Population))*100),digits = 1) , min = 0, max =100,label= "% Population",gaugeSectors(success = c(0,50), warning = c(51,70), danger = c(71, 100)))
    
 # }
  
  
})

```

Population Barchart {data-navmenu="Menu"}
======================================================================================

Column 1
----------------------------------------------------------------------------

### Barchart of States in Nigeria
Data Source : https://open.africa/dataset/population

```{r}
# Population Barchart {data-navmenu="Menu"} to used the navbar as a "menu"

renderPlot({
  # For barchart
  q = ggbarplot(nig_pop, y="Population",x="State",fill = "State",color ="white",ggtheme = theme_gray())
  
  ggpar(q, x.text.angle=90, legend = "none", )
  
  
})

```


Doughnutchart of States in Nigeria {data-navmenu="Menu"}
======================================================================================

### Population Doughnutchart

```{r}
#Doughnutchart of States in Nigeria {data-navmenu="Menu"}

renderPlot({
  # For adding percentage of each values
  #labs <- paste0(nig_pop$State, " (", (nig_pop$Population/sum(nig_pop$Population))*100, "%)")
  p = ggdonutchart(nig_pop, "Population","State",fill = "State",color ="white",ggtheme = theme_gray(),lab.pos="in")
  #ggdonutchart(nig_pop, "Population",label = labs,fill = "State",color ="white")
  
  ggpar(p, legend = "none")
})

```


Piechart of States in Nigeria{data-navmenu="Menu"} 
======================================================================================


### Population Piechart Plot

```{r}
# Piechart of States in Nigeria {data-navmenu="Menu"}

renderPlot({
  # For Pie chart
  ggpie(nig_pop, "Population","State",fill = "State",color ="white",ggtheme = theme_gray())
  
})

```


Ballonchart of States in Nigeria {data-navmenu="Menu"}
======================================================================================

### Population Ballonchart Plot

```{r}
renderPlot({
  
  ggballoonplot(nig_pop2,ggtheme = theme_classic(), fill = "red")
  
})

```


```{r}
#rmarkdown::run("Nigeria_Population.Rmd")
```
