---
title: "SVM_2"
author: "Johnson Adebayo"
date: "8/10/2020"
output: html_document
---

# https://www.edureka.co/blog/support-vector-machine-in-r/

# Package Loading
```{r}
library(caret)

```

```{r}

heart1 <- read.csv("heart.csv")
```

```{r}
View(heart1)

```


```{r}
str(heart1)

```

# Data Splitting
```{r}

intrain <- createDataPartition(y = heart1$target, p= 0.7, list = FALSE)
training <- heart1[intrain,]
testing <- heart1[-intrain,]
```

# Data Cleaning and Exploration
```{r}
dim(training)
dim(testing)

```

# Checking for missing values NA
```{r}
#anyNA(heart1)
sapply(heart1, function(x){ sum(is.na(x))})
```


```{r}
summary(heart1)

```

## Converting the 'target' variable from integer to categorical variable
```{r}
# training[["V14"]] = factor(training[["V14"]])

training$target <- as.factor(training$target)
testing$target <- as.factor(testing$target)

```


# Fitting the SVM Model 

## Creating the control of the train 'model'
```{r}
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)


```


```{r}
svm_linear <- train(target~., data = training, method = "svmLinear", preProcess=c("center","scale"), trControl =trctrl, tuneLength=10 )

```

## Checking the result of the model
```{r}
svm_linear
```

# Making Prediction with the model 'svm_linear'
```{r}
test_prediction <- predict(svm_linear, testing)
confusionMatrix(table(test_prediction, testing$target))

```

## Alternatively
```{r}
testing1 <- testing[c(1:13)]

```


```{r}
test_prediction2 <- predict(svm_linear, newdata = testing1)
confusionMatrix(table(test_prediction2, testing$target))

```

# Improving the Model Result

## Hyperparameter Tuning e.g. Grid tuning
```{r}
# 'C' is the Column
grid <- expand.grid(C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2,5))

#grid <- expand.grid(nprune = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2,5),degree = c(1, 2, 3, 4))

```


```{r}
grid <- expand.grid(C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2,5))
svm_Linear_Grid3 <- train(target ~., data = training, method = "svmLinear",
trControl=trctrl,
preProcess = c("center", "scale"),
tuneGrid = grid,
tuneLength = 10)
svm_Linear_Grid3
plot(svm_Linear_Grid3)

```

# Making Prediction with the improved model
```{r}
test_prediction3 <- predict(svm_Linear_Grid3, testing)

confusionMatrix(table(test_prediction3, testing$target))

```


```{r}
((0.8333-0.8222)/0.8222)*100

```

## The result of the improved model (Grid tuning) shows that there is improved in the result by 1.35%

```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```




